Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
added the description of more benchmarks

\subsection{Solution generalisation} 
Given the large soloution space to be searched during the inductive
synthesis phase, we parametrise the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesise a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e. a solution in the original search space).

@@

Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
(blocks 1 to 5):

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming a plan't
precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

@@

Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a 
metal ball hanged in air. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude. 
\textit{Automotive Cruise System} plant describes the model that represents 
the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the 
longitudinal motion model of a helicopter. 
\textit{Inverted Pendulum} plant describes the model of a pendulum 
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides the model for which 
a given object is suspended via a magnetic field. 
\textit{Magnetized Pointer} plant describes a model rotated through interaction 
with magnetic fields, which is typically employed in analog gauges and indicators.

@@

\caption{Test suite for space-state synthesis}

>>>>

\subsection{Solution generalisation} 
Given the large soloution space to be searched during the inductive
synthesis phase, we parametrise the target language, which induces a
lattice of progressively more expressive languages.  This enables us 
to start by attempting to synthesise a program at the lowest point on this lattice
and increase the parameters of the language until we reach a point at
which the synthesis succeeds. Whenever we manage to synthesise
a candidate solution at some lower point on the lattice, 
we apply generalisation to obtain a full solution.

@@

Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
The check that these assumptions are sound 
is performed later by the {\sc complete} and {\sc sampling} 
validation stages.

@@

Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
metal ball hanged in air via a magnetic field . 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

\textit{Automotive Cruise System} plant describes a physical model that represents 
the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the 
longitudinal motion model of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides the physical model for which 
a given object is suspended via a magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
with magnetic fields (typically employed in analog gauges and indicators).
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a physical model to read and write data 
on a storage device in the computer.
\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
for the yaw angle dynamics of a US warship USCG Cutter Tampa.

@@

\caption{Benchmarks for State-Space Physical Plants.}
